My title

### 2024-09-24 paper/paper.qmd
add "weakness"; aad personal information

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jianing Li
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

# Discussion

@@

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

## Posterior predictive check

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jianing Li
thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)

@@

@@

# Discussion {#sec-discussion}

@@

## Weaknesses and next steps
A limitation of this analysis is that the data analyzed does not reflect the entire Toronto homeless population. The database used only includes people who use City of Toronto-funded overnight shelter services and fails to reflect people who spend the night outdoors or use other homeless services. According to the most recent Street Needs Assessment, approximately 18% of the homeless population is not included in the data[@torontosheltersystem].

Future directions for improvement should include expanding the data scope of the analysis to include people who spend the night outdoors and use shelters that are not funded by the Government of Toronto, in order to provide a more complete picture of homelessness in Toronto. This will help fill data gaps and support more effective policy decisions.

@@
